### 2021-04-23 submission/manuscript.Rmd
Generate latest draft with updated figures

**1-day laxative treatment results in transient *C. difficile* colonization and minor microbiota disruption**
  + Explain motivation for experiment, set-up of experiment (Fig. 4A). 
  + Transient *C. difficile* colonization in 1-day PEG treated mice with all PEG mice clearing by 7dpi (Fig. 4B)
  + PCoA results (Day has larger R2 than treatment group). PEG mice are closer to baseline communites after 7-day period (Fig. 4C)
  + Shannon results show alpha diversity is only transiently disrupted (Fig. 4D)
  + Highlight bacteria that are disrupted by PEG or clindamycin treatment but recover within 7 days (Fig. 4E)

**Post-CDI laxative treatment disrupts clearance in clindamycin-treated mice regardless of whether an FMT is also administered**
  + Reiterate motivation for experiment. Saw only a transient microbiota disruption with 1-day PEG treatment alone. Also, see if adding FMT helps with clearance, mention groups have been using PEG or Abx/PEG treatments as a tool to engraft mice with human bacteria communities. Set up of experiment (Fig. 5A).
  + Prolonged *C. difficile* colonization in post-CDI PEG treated mice (Fig. 5B)
  + FMT appears to partially restore alpha diversity (Shannon, but not richness Fig. 5C-D)
  + PCoA (necessary?) Could comment on the clustering of Clindamycin and PEG-treated mice that received FMT (Fig. 5E)
  + Only 2 genera significantly impacted by FMT treatment, likely not as important for clearance (Fig. 5F)
  + Bacteria that consistently differ between groups over time, associated with prolonged colonization (Fig. G)

@@

* Figure 6. Specific microbiota features associated with prolonged *C. difficile* colonization in PEG treated mice.

* Figure S2. Specific OTUs associated with clearance that are mostly absent in mice with prolonged *C. difficile* colonization.
  + Ex. *Muribaculum intestinale*.

@@

\newpage
\includegraphics{figure_5_16S.pdf}
**Figure 5. 1-day PEG treatment post C. difficile challenge prolongs colonization regardless of whether an FMT is also administered.** A. PCoA of all groups + FMT plotted over time. Opacity of points reflects time point. B. Relative abundance of genera significantly different over multiple time points post FMT or PBS treatment, plotted over time. Limit of detection is .1%. C. Relative abundances of top 6 significant genera ranked by number of days significant, plotted over time. Limit of detection is .1%.

@@

\includegraphics{figure_6.pdf}
**Figure 6. Specific microbiota features associated with prolonged *C. difficile* colonization in PEG treated mice.** A. 
\newpage

\includegraphics{figure_7.pdf}
**Figure 7. Schematic summarizing findings.** A. 
\newpage

@@

\includegraphics{figure_S2.pdf}
**Figure S2. Specific OTUs associated with clearance that are mostly absent in mice with prolonged *C. difficile* colonization. Ex. *Muribaculum intestinale*.** A. 
\newpage

>>>>

**1-day laxative treatment results in transient *C. difficile* colonization and minor microbiota disruption**

* Draft of results
  + Explain motivation for experiment, set-up of experiment (Fig. 4A). 
  + Transient *C. difficile* colonization in 1-day PEG treated mice with all PEG mice clearing by 7dpi (Fig. 4B)
  + PCoA results (Day has larger R2 than treatment group). PEG mice are closer to baseline communites after 7-day period (Fig. 4C)
  + Shannon results show alpha diversity is only transiently disrupted (Fig. 4D)
  + Highlight bacteria that are disrupted by PEG or clindamycin treatment but recover within 7 days (Fig. 4E)

**Post-CDI laxative treatment disrupts clearance in clindamycin-treated mice regardless of whether an FMT is also administered**

* Draft of results
  + Reiterate motivation for experiment. Saw only a transient microbiota disruption with 1-day PEG treatment alone. Also, see if adding FMT helps with clearance, mention groups have been using PEG or Abx/PEG treatments as a tool to engraft mice with human bacteria communities. Set up of experiment (Fig. 5A).
  + Prolonged *C. difficile* colonization in post-CDI PEG treated mice (Fig. 5B)
  + FMT appears to partially restore alpha diversity (Shannon, but not richness Fig. 5C-D)
  + PCoA (necessary?) Could comment on the clustering of Clindamycin and PEG-treated mice that received FMT (Fig. 5E)
  + Only 2 genera significantly impacted by FMT treatment, likely not as important for clearance (Fig. 5F)
  + Bacteria that consistently differ between groups over time, associated with prolonged colonization (Fig. G)

@@

@@

\newpage
\includegraphics{figure_6.pdf}
**Figure 6. 1-day PEG treatment post C. difficile challenge prolongs colonization regardless of whether an FMT is also administered.** A. PCoA of all groups + FMT plotted over time. Opacity of points reflects time point. B. Relative abundance of genera significantly different over multiple time points post FMT or PBS treatment, plotted over time. Limit of detection is .1%. C. Relative abundances of top 6 significant genera ranked by number of days significant, plotted over time. Limit of detection is .1%.

@@

\includegraphics{figure_7.pdf}
**Figure 7. Specific microbiota features associated with prolonged *C. difficile* colonization in PEG treated mice.** A. 
\newpage

\includegraphics{figure_8.pdf}
**Figure 8. Schematic summarizing findings.** A. 
\newpage

@@

\includegraphics{figure_S2.pdf}
**Figure S2. Impact of PEG treatment on the mucosal microbiota is greatest 6 days post-infection**  
\newpage

\includegraphics{figure_S3.pdf}
**Figure S3. *C. difficile* challenge does not enhance the disruptive effect of PEG on the microbiota.** A. 
\newpage

\includegraphics{figure_S4.pdf}
**Figure S4. Specific OTUs associated with clearance that are mostly absent in mice with prolonged *C. difficile* colonization. Ex. *Muribaculum intestinale*.** A. 
\newpage

### 2021-04-23 submission/manuscript.tex
Generate latest draft with updated figures

\textbf{1-day laxative treatment results in transient \emph{C.
difficile} colonization and minor microbiota disruption} + Explain
motivation for experiment, set-up of experiment (Fig. 4A). + Transient
\emph{C. difficile} colonization in 1-day PEG treated mice with all PEG
mice clearing by 7dpi (Fig. 4B) + PCoA results (Day has larger R2 than
treatment group). PEG mice are closer to baseline communites after 7-day
period (Fig. 4C) + Shannon results show alpha diversity is only
transiently disrupted (Fig. 4D) + Highlight bacteria that are disrupted
by PEG or clindamycin treatment but recover within 7 days (Fig. 4E)

\textbf{Post-CDI laxative treatment disrupts clearance in
clindamycin-treated mice regardless of whether an FMT is also
administered} + Reiterate motivation for experiment. Saw only a
transient microbiota disruption with 1-day PEG treatment alone. Also,
see if adding FMT helps with clearance, mention groups have been using
PEG or Abx/PEG treatments as a tool to engraft mice with human bacteria
communities. Set up of experiment (Fig. 5A). + Prolonged \emph{C.
difficile} colonization in post-CDI PEG treated mice (Fig. 5B) + FMT
appears to partially restore alpha diversity (Shannon, but not richness
Fig. 5C-D) + PCoA (necessary?) Could comment on the clustering of
Clindamycin and PEG-treated mice that received FMT (Fig. 5E) + Only 2
genera significantly impacted by FMT treatment, likely not as important
for clearance (Fig. 5F) + Bacteria that consistently differ between
groups over time, associated with prolonged colonization (Fig. G)

@@

\begin{itemize}
\item
  Figure 6. Specific microbiota features associated with prolonged
  \emph{C. difficile} colonization in PEG treated mice.
\item
  Figure S2. Specific OTUs associated with clearance that are mostly
  absent in mice with prolonged \emph{C. difficile} colonization.

  \begin{itemize}
  \tightlist
  \item
    Ex. \emph{Muribaculum intestinale}.
  \end{itemize}
\end{itemize}

@@

\includegraphics{figure_5_16S.pdf} \textbf{Figure 5. 1-day PEG treatment
post C. difficile challenge prolongs colonization regardless of whether
an FMT is also administered.} A. PCoA of all groups + FMT plotted over
time. Opacity of points reflects time point. B. Relative abundance of
genera significantly different over multiple time points post FMT or PBS
treatment, plotted over time. Limit of detection is .1\%. C. Relative
abundances of top 6 significant genera ranked by number of days
significant, plotted over time. Limit of detection is .1\%.

@@

\includegraphics{figure_6.pdf} \textbf{Figure 6. Specific microbiota
features associated with prolonged \emph{C. difficile} colonization in
PEG treated mice.} A. \newpage

\includegraphics{figure_7.pdf} \textbf{Figure 7. Schematic summarizing
findings.} A. \newpage

@@

\includegraphics{figure_S2.pdf} \textbf{Figure S2. Specific OTUs
associated with clearance that are mostly absent in mice with prolonged
\emph{C. difficile} colonization. Ex. \emph{Muribaculum intestinale}.}
A. \newpage

>>>>

\textbf{1-day laxative treatment results in transient \emph{C.
difficile} colonization and minor microbiota disruption}

\begin{itemize}
\tightlist
\item
  Draft of results

  \begin{itemize}
  \tightlist
  \item
    Explain motivation for experiment, set-up of experiment (Fig. 4A).
  \item
    Transient \emph{C. difficile} colonization in 1-day PEG treated mice
    with all PEG mice clearing by 7dpi (Fig. 4B)
  \item
    PCoA results (Day has larger R2 than treatment group). PEG mice are
    closer to baseline communites after 7-day period (Fig. 4C)
  \item
    Shannon results show alpha diversity is only transiently disrupted
    (Fig. 4D)
  \item
    Highlight bacteria that are disrupted by PEG or clindamycin
    treatment but recover within 7 days (Fig. 4E)
  \end{itemize}
\end{itemize}

\textbf{Post-CDI laxative treatment disrupts clearance in
clindamycin-treated mice regardless of whether an FMT is also
administered}

\begin{itemize}
\tightlist
\item
  Draft of results

  \begin{itemize}
  \tightlist
  \item
    Reiterate motivation for experiment. Saw only a transient microbiota
    disruption with 1-day PEG treatment alone. Also, see if adding FMT
    helps with clearance, mention groups have been using PEG or Abx/PEG
    treatments as a tool to engraft mice with human bacteria
    communities. Set up of experiment (Fig. 5A).
  \item
    Prolonged \emph{C. difficile} colonization in post-CDI PEG treated
    mice (Fig. 5B)
  \item
    FMT appears to partially restore alpha diversity (Shannon, but not
    richness Fig. 5C-D)
  \item
    PCoA (necessary?) Could comment on the clustering of Clindamycin and
    PEG-treated mice that received FMT (Fig. 5E)
  \item
    Only 2 genera significantly impacted by FMT treatment, likely not as
    important for clearance (Fig. 5F)
  \item
    Bacteria that consistently differ between groups over time,
    associated with prolonged colonization (Fig. G)
  \end{itemize}
\end{itemize}

@@

@@

\includegraphics{figure_6.pdf} \textbf{Figure 6. 1-day PEG treatment
post C. difficile challenge prolongs colonization regardless of whether
an FMT is also administered.} A. PCoA of all groups + FMT plotted over
time. Opacity of points reflects time point. B. Relative abundance of
genera significantly different over multiple time points post FMT or PBS
treatment, plotted over time. Limit of detection is .1\%. C. Relative
abundances of top 6 significant genera ranked by number of days
significant, plotted over time. Limit of detection is .1\%.

@@

\includegraphics{figure_7.pdf} \textbf{Figure 7. Specific microbiota
features associated with prolonged \emph{C. difficile} colonization in
PEG treated mice.} A. \newpage

\includegraphics{figure_8.pdf} \textbf{Figure 8. Schematic summarizing
findings.} A. \newpage

@@

\includegraphics{figure_S2.pdf} \textbf{Figure S2. Impact of PEG
treatment on the mucosal microbiota is greatest 6 days post-infection}\\
\newpage

\includegraphics{figure_S3.pdf} \textbf{Figure S3. \emph{C. difficile}
challenge does not enhance the disruptive effect of PEG on the
microbiota.} A. \newpage

\includegraphics{figure_S4.pdf} \textbf{Figure S4. Specific OTUs
associated with clearance that are mostly absent in mice with prolonged
\emph{C. difficile} colonization. Ex. \emph{Muribaculum intestinale}.}
A. \newpage
